The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-31 dit-paper_ieee.tex
made the bibliography style ieeetran
Added reference to Navet paper

\author{
\IEEEauthorblockN{Thomas Chapeaux and Paul Rodriguez}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
Email: tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
\and
\IEEEauthorblockN{Laurent George and ???}
\IEEEauthorblockA{ECE Paris\\
Email}
}
\maketitle

@@

Future works could also study the shape of the C-space and how it is affected by some factors. An
interesting path would be the effect of the CDF on the number of constraints describing the C-space,
as we know that in the implicit case this description is simple ($U_{tot} \leqslant 1$). While we
quantified the feasibility gain by looking at the ratio between sizes of C-space, another approach
would be to look at the ratio between the minimal distance of the border of the C-space, which would
give a lower bound of the gain given by the offsets.

>>>>

\author{
\IEEEauthorblockN{Thomas Chapeaux and Paul Rodriguez}
\IEEEauthorblockA{Universit\'{e} Libre de Bruxelles\\
tchapeau@ulb.ac.be, paurodri@ulb.ac.be}
\and
\IEEEauthorblockN{Laurent George and ???}
\IEEEauthorblockA{ECE Paris\\
lgeorge@ece.fr}
}
\maketitle

@@

Future works could also repeat the simulation of section~\ref{sct:expCspaceGain} with the algorithm described in \cite{grenier2008pushing}, which determine offset values with optimal feasibility. The
feasibility gain could then be expressed using the C-space.

Another direction is to study the shape of the C-space and how it is affected by some factors. An
interesting path would be the effect of the CDF on the number of constraints describing the C-space,
as we know that in the implicit case this description is simple ($U_{tot} \leqslant 1$). While we
quantified the feasibility gain by looking at the ratio between sizes of C-space, another approach
would be to look at the ratio between the minimal distance of the border of the C-space, which would
give a lower bound of the gain given by the offsets.
